gilmore-nysds-2016

### 2016-08-11 nysds-2016/gilmore-nysds-2016.Rmd
1st full draft of NYSDS 16

**Curating identifiable data**

@@

<div class="centered">
<a href="https://databrary.org/access/guide/investigators/release/release-levels.html">
<img src="img/release-levels.jpg">
</a>
</div>

@@

<div class="centered">
<video width="640" height="480" controls>
  <source src="https://nyu.databrary.org/slot/223/-/asset/47075/download?inline=true" type="video/mp4">
Your browser does not support the video tag.
</video>
</div>
</iframe>

@@

<div class="centered">
<img src="http://www.psyrecon.de/uploads/pics/psychophysiologischeVariablen_01.jpg">
</div>

@@

- Heart rate, skin conductance, brain activation
- Eye position, diameter
- Body position, movement

@@

## Common metadata representation makes search, filtering easy

<div class="centered">
<img src="img/search=1-2-y-olds.jpg">
**"Show me all the datasets that have videos of 1-2 year-old children"**
</div>

@@

- Video uniquely captures complexity & richness of behavior
- Video captures vital methodological details
- Identifiable video (and other data) can be shared securely and ethically
- Preparing to share reduces the burden
- Video data sharing essential for a reproducible behavioral science

>>>>

## Curating identifiable data with Databrary

<div class="centered">
<img src="img/databrary-leaf-large.png" height=450>
</div>

@@

<div class="centered">
<a href="https://databrary.org/access/guide/investigators/release/release-levels.html">
<img src="img/release-levels-revised.jpg" width=1000px>
</a>
</div>

@@

<div class="centered">
<video width="700" height="550" controls>
  <source src="https://nyu.databrary.org/slot/11652/307774,376273/asset/47075/download?inline=true" type="video/mp4">
Your browser does not support the video tag.
</video>
</div>
</iframe>

@@

<div class="centered">
<a href="http://www.psyrecon.de/uploads/pics/psychophysiologischeVariablen_01.jpg">
<img src="http://www.psyrecon.de/uploads/pics/psychophysiologischeVariablen_01.jpg" height=500px>
</a>
</div>

@@

- Heart rate, skin conductance, brain activation
- Eye position, diameter
- Body position, movement
- Coming soon: Visualizing Datavyu tags within Databrary

@@

## Searching, filtering by participant characteristics

<div class="centered">
<img src="img/search-1-2-y-olds.jpg" height=450px>
</div>

@@

- Video uniquely captures complexity & richness of behavior
- Video captures vital methodological details
- Identifiable video (and other data) can be shared securely and ethically
- Preparing to share reduces the burden
- Video data sharing essential for a reproducible science
